---
title: "Statistical Tools in MATH4753JONE24"
author: "Preston Jones"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Statistical Tools in MATH4753JONE24}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This vignette provides an overview of the MATH4753JONE24 package, which includes a suite of functions designed to facilitate common statistical analyses and demonstrations. These tools are particularly useful for educational purposes and real-world data analysis scenarios.

# Package Functions

The package includes several functions, which we will demonstrate with practical examples below.

```{r}
library(MATH4753JONE24)
```


## 1. Maximum Likelihood Estimation for Normal Distribution

The `mle_normal` function estimates the mean and standard deviation of a normally distributed sample.

```{r}
# Simulating normal distribution data
sample_data <- rnorm(100, mean = 50, sd = 10)
estimates <- mle_normal(sample_data)
print(estimates)
```

## 2. Simulating Binomial Experiments

The `mybin` function simulates binomial experiments and visualizes the distribution of successes.

```{r}
proportions <- mybin(100, 10, 0.7)
```

## 3. Demonstrating the Central Limit Theorem

`myclt` demonstrates the Central Limit Theorem (CLT) by taking samples from a uniform distribution.

```{r}
means <- myclt(n = 10, iter = 1000, a = 0, b = 5)
hist(means, main="Sample Means (CLT)")
```

## 4. Bootstrapping for Confidence Intervals

`myboot2` uses bootstrapping to estimate confidence intervals for a specified statistic.

```{r}
set.seed(68)
sample_data <- rnorm(20, mean = 10, sd = 4)
bootstrap_results <- myboot2(x = sample_data)
print(bootstrap_results)
```

# Conclusion

MATH4753JONE24 provides powerful statistical tools that are essential for students and researchers working with statistical data. This vignette has introduced these tools and shown how to use them effectively in various statistical tasks.



